---
title: "Simpsons' Guest Appearances are Growing"
author: "Adaptation of Gil Henriques' Simpsons Plot, by Evangeline Reynolds"
date: "5/18/2018"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["kunoichi", "ninjutsu"]
    nature:
      ratio: "16:9"
      beforeInit: "https://platform.twitter.com/widgets.js"
      highlightLines: true
---




```{r, message = F, warning = F, include = F}
source("https://raw.githubusercontent.com/EvaMaeRey/little_flipbooks_library/master/xaringan_reveal_parentheses_balanced.R")
```


```{r, include=F}
knitr::opts_chunk$set(fig.width = 9, message = F, warning = F, 
                      comment = "", cache = F, fig.height = 5)
```


---

# The original

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">📈 I learned a lot doing this week&#39;s <a href="https://twitter.com/hashtag/TidyTuesday?src=hash&amp;ref_src=twsrc%5Etfw">#TidyTuesday</a>. I had to make the axes and the lines connecting the points look hand-drawn (it takes some jittering!), and learn how to put a figure in the background. Happy with the result! Code below.<a href="https://twitter.com/hashtag/dataviz?src=hash&amp;ref_src=twsrc%5Etfw">#dataviz</a> <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> <a href="https://twitter.com/hashtag/ggplot2?src=hash&amp;ref_src=twsrc%5Etfw">#ggplot2</a> <a href="https://twitter.com/R4DScommunity?ref_src=twsrc%5Etfw">@R4DScommunity</a> <a href="https://t.co/Gr0w37pbt9">pic.twitter.com/Gr0w37pbt9</a></p>&mdash; Gil Henriques 🌹 (@_Gil_Henriques) <a href="https://twitter.com/_Gil_Henriques/status/1166373844040335360?ref_src=twsrc%5Etfw">August 27, 2019</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


---

# Loading packages

```{r}
library(tidyverse)
```


---

# Data cleaning

---

```{r}
url <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-08-27/simpsons-guests.csv"
raw <- read_delim(file = url, delim = "|", quote = "") %>%
  mutate(number = strsplit(as.character(number), "; "))
```


---

```{r cleaning, echo = F}
raw %>%
  unnest() %>% # Splits rows that contain multiple episodes into multiple rows
  mutate(season = as.numeric(season)) %>% 
  group_by(season) %>% 
  summarize(guests_per_episode = 
              n_distinct(guest_star) /
              n_distinct(number)) ->
clean_data
```


`r apply_reveal("cleaning")`

---

# Attention to detail:  "Hand drawing"


One thing that is so charming about this plot is the feeling that Bart Simpson has hand-drawn the figure.  

Gil writes: *I want the axes and the line connecting the points to look hand-drawn, so I will use geom_line + jitter to draw them*


---

# spline() to connect points

He uses the spline function, which makes a smooth connection between points, rather than sharp, as a human might do in a rush.


Here is the function: 

spline(x, y = NULL, n = 3*length(x), method = "fmm",
       xmin = min(x), xmax = max(x), xout, ties = mean)

And the description:

"Perform cubic (or Hermite) [spline interpolation](https://en.wikipedia.org/wiki/Spline_interpolation) of given data points, returning either a list of points obtained by the interpolation or a function performing the interpolation."


---

```{r shaky_hand, echo = F}
as.data.frame(spline(x = clean_data$season, 
                     y = clean_data$guests_per_episode, 
                     method = "natural")) ->
  spline_int
```

`r apply_reveal("shaky_hand")`


---

# "Hand drawn" axes with position_jitter()

Then Gil also creates mini datasets for hand drawn axes x and y.  He creates straight horizontal and vertical lines, segmented into small pieces.  He plots these mini data sets with geom_line where the position is jittered.   




---

```{r axes, echo = F}
data.frame(x = seq(from = 0, to = 30, by = 1), 
           y = rep(0, 31)) -> 
  drawn.x.axis
data.frame(x = rep(0, 21), 
           y = seq(from = 0, to = 4, by = 0.2)) -> 
  drawn.y.axis
```

`r apply_reveal("axes")`




---
# Plotting


---


```{r plotting, echo = F}
clean_data %>% 
  ggplot() + 
  aes(x = season) +
  aes(y = guests_per_episode) +
  geom_point(size = 4, color = "snow3") + 
  geom_line(data = spline_int, 
            mapping = aes(x = x, y = y), 
            color = "snow3", size = 0.8,
            position = position_jitter(w = 0.05, h = 0.05)) +
  geom_line(data = drawn.x.axis, 
            mapping = aes(x = x, y = y), 
            color = "snow3", size = 0.8,
            position = position_jitter(w = 0.0, h = 0.05)) +
  geom_line(data = drawn.y.axis, 
            mapping = aes(x = x, y = y), 
            color = "snow3", size = 0.8,
            position = position_jitter(w = 0.05, h = 0.0)) +
  labs(y = "Guests per episode") + 
  labs(x = "Season") + 
  labs(title = "The number of guest stars in\nthe Simpsons is increasing") +
  labs(caption = "@_Gil_Henriques for #TidyTuesday") +
  ylim(-0.1, 4.3) + 
  xlim(-0.1, 30.5) + 
  theme_void() +
  theme(axis.text = element_text(size = 15, 
                                   color = "snow3")) +
  theme(axis.title = element_text(size = 20, color = "snow3")) +
  theme(plot.title = element_text(size = 25, face = "bold", 
                                  color = "snow3", 
                                  hjust = 0.5)) +
  theme(plot.caption = element_text(color = "snow3")) +
  theme(plot.margin = margin(t = 1, r = 3, b = 1, l = 1, "cm"))  +
  theme(axis.title.y = element_text(angle = 90)) ->  
plot 
```

`r apply_reveal("plotting")`

---

# Adding background

---

```{r simpsons, echo = F, eval = F, fig.width=9, fig.height=5}
simpsons_gif_url <- "https://github.com/GilHenriques/TidyTuesdays/blob/master/2019-08-27%20Simpsons%20guest%20stars/chalkboard_simpsons.gif?raw=true"
plot %>% 
  ggimage::ggbackground(
    background = simpsons_gif_url, 
    by = "height")
```

`r apply_reveal("simpsons")`


---

# Changes from the [original](https://github.com/GilHenriques/TidyTuesdays) and notes to self


- I use [slow ggplot principles](https://evamaerey.github.io/ggplot_flipbook/ggplot_flipbook_xaringan.html#3) to provide maximal feedback for each step of the build. 
- Fonts are still tricky to manage across platforms and in the flipbook setting, so sadly I don't do anything with them, and a less charming plot results.
- I changed the text color to be off white instead of white, so that you can see it against the theme_void() white background
- There seems to be some problem with the display when there are list columns in data relates to square brackets. hmmmmm...
- This should be included in [TidyTuesday walk-throughs](https://evamaerey.github.io/tidytuesday_walk_through/tidytuesday_highlights.html#1) at some point.






---


```{css, eval = TRUE, echo = F}
.remark-code{line-height: 1.5; font-size: 65%}
```
  
